{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
added a remark in introduction and shortened a footnote

The notion of confidentiality that is used in most work in the area of information-flow security is \textit{noninterference}.
This policy is defined in various ways but the essence is, that it requires 'that secret information
[do] not affect [the] publicly observable behavior of a system'\cite{Zdancewic04}. For most real world
applications this policy is far too strict, because it forbids useful programs like password checkers.\footnote{For a
password checker its necessary to reveal whether the user input was correct or not.} Approaches that allow
controlled release of information are called declassification. The kinds of declassification are \textit{what}
information is released, \textit{who} released this information, \textit{where} in the system the information
is released and \textit{when} the information is released (c.f. \cite{Sabelfeld05}). For these approaches it is necessary that an
active attacker can only know as much as a passive attacker.

>>>>

The notion of confidentiality that is used in most work in the area of information-flow security is \textit{noninterference}.
This policy is defined in various ways but the essence is, that it requires 'that secret information
[do] not affect [the] publicly observable behavior of a system'\footnote{Even wen the attacker has full access to the
source code of the program.}\cite{Zdancewic04}. For most real world
applications this policy is far too strict, because it forbids useful programs like password checkers.\footnote{A
password checker needs to reveal whether the user input was correct or not.} Approaches that allow
controlled release of information are called declassification. The kinds of declassification are \textit{what}
information is released, \textit{who} released this information, \textit{where} in the system the information
is released and \textit{when} the information is released (c.f. \cite{Sabelfeld05}). For these approaches it is necessary that an
active attacker can only know as much as a passive attacker.
